Algomusicology, ?, Profit

### 2016-04-02 paper.tex
Add introduction.

\title{Algomusicology, ???, Profit}
%\subtitle{Subtitle Text, if any}

@@

\begin{abstract}
    In this paper I propose a novel method for converting algomusicology into profit. While my particular example
    is slightly tongue-in-cheek, my serious point is that algorithmic composition can help us deconstruct and
    disrupt traditional notions of musical authorship.
\end{abstract}

@@

>>>>

\title{Algomusicology, ?, Profit}
%\subtitle{Subtitle Text, if any}

@@

\begin{abstract}
    In this paper I propose a novel method for converting algomusicology into profit. While my particular example
    is tongue-in-cheek, my serious point is that algorithmic composition can help us deconstruct and disrupt
    traditional notions of musical authorship.
\end{abstract}

@@

The Underpants Gnomes are renowned for their business plan:
\begin{itemize}
    \item Collect underpants
    \item ?
    \item Profit
\end{itemize}

Art critics, literary critics, Algomusicologists have a challenge in common with the Underpants Gnomes, we may have
collected a vast amount of underpants/art/users, but how are we to turn that into profit? Less glibly, is algomusicology
doomed to be a mere observer and explainer of musical practice, or might it become an active participant? Computer science is
able to influence industry, though that might take longer than we'd like \footnote{Alonzo Church developed the
lambda calculus in the 1930s. Java gained lambda expressions in 2015.}. Can algomusicology influence music?

The examples in this paper are all written in Clojure, dialect of Lisp. I also rely on Leipzig, a small music theory
library written in Clojure and Midje, for music theoretical functions, and Midje, a unit testing library, for assertions.
